\chapter{Conclusion}
\label{cha:conclusion}
This thesis report gives a detailed background on the mathematical security aspects of 
Shamir secret sharing, and necessary required literature is reviewed by recalling a 
very recent variant of PVSS, more precisely, PPVSS is recalled along with an example 
candidate $\Lambda_{RO}$ proposed in \cite{cryptoeprint:2025/576}. And further, the PPVSS is generalized 
to 3PVSS (/PPPVSS) in this thesis where one has to share multiple 
secrets packed in a single polynomial, and subsequently, two candidate 3PVSS schemes 
are proposed in this report. Also, the security guarantees of both candidates are shown.\par

The goal of this thesis is to revisit the state-of-the-art randomness beacon protocol 
based on PVSS, ALBATROSS \cite{cryptoeprint:2020/644}. A significant bottleneck of 
ALBATROSS is in its \textit{Reveal} phase, as name suggests it reveals the dealers' secrets 
and verifies the validity of the revealed secrets. With 3PVSS, it is shown in this 
report that ALBATROSS can be further improved in efficiency in many cases. The report 
also highlights the cases where our protocol can underperform ALBATROSS. The security 
properties of our protocol is briefly discussed which strongly depends on the 3PVSS, 
$\Lambda_{RO}$, mathematical security guarantees.\par

When trying to prove the mathematical security guarantees of $\Lambda_{RO}^{packed}$,  
the underlying mathematical proof system is acknowledged. So, before delving into the 
security proof of $\Lambda_{RO}^{packed}$, its underlying proof system with its properties 
is written down formally, which were essential and desirable to explain its 
achievable security. Though $\Lambda_{RO}^{packed}$ is more efficient than the first 
proposed 3PVSS, $\Lambda_{RO}'$, it is essential to note that $\Lambda_{RO}'$ is tailored 
for specific applications where using $\Lambda_{RO}^{packed}$ may not be suitable. Also, 
the discussed security guarantees of $\Lambda_{RO}'$ in this report is trivially 
realized from the security guarantees of $\Lambda_{RO}$. For completeness, both proposed candidates 
for 3PVSS computation and communication costs are discussed.\par

The new proof system $\pi_{mod-PDL}^{AoK}$ on which $\Lambda_{RO}^{packed}$ is based on, 
can be further improved. So in future, one can think if a new proof system that can be built 
to improve not only $\Lambda_{RO}^{packed}$ but also the state-of-the-art PVSS $\Pi_{S}$ \cite{cryptoeprint:2023/1669}, 
which can lead to revisiting all the applications built so far with the aforementioned schemes.\par

To conclude, this thesis gives enough background and literature review required to 
progress till the end. An extension of newly proposed variant of PVSS is proposed and 
two candidate examples with their security proofs are given. An application based on PVSS 
is revisited, where its bottleneck is taken into account, and improved its performance 
in many cases. Especially, the communication cost of the new protocol is always less in 
contrast to ALBATROSS.


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End: 
