\section{Packed Shamir Secret Sharing}
\label{sec:packed-shamir}
$(n,t,\ell)$-Packed Shamir secret sharing (\cite{../10.1145/129712.129780},\cite{../crypto-1984-905})
 scheme is a threshold secret sharing scheme which is a variant of $(n,t)$-Shamir's 
 secret sharing scheme \cite{../10.1145/359168.359176} where $n>t+\ell-1$. In a nutshell, the $t+\ell-1$ 
 degree secret polynomial with coefficients in $\mathbb{Z}_q$ which evaluates to $\ell$ 
 secrets is secret shared amongst $n$ parties such that any $t+\ell$ parties can 
 reconstruct back the secret polynomial. Recall that Shamir's secret sharing scheme 
 requires at least $t+1$ parties to reconstruct the secret polynomial in contrast to 
 the $t+\ell$ parties in the Packed Shamir secret sharing scheme. The scheme is
 summarized in the Figure \ref{../fig:packed-shamir}.
\input{figures/packed_shamir.tex}

One can observe that all the secret shares of a secret polynomial chosen by the dealer form a codeword in 
$[n,t+l,n-t-l+1]-$RS code. If the adversary is malicious and can corrupt at most $t$ parties, then from 
corollary \ref{../cor:detectable-correctable RS}, the honest shareholders can detect the errors if 
$2t\leq n-l$ and moreover all such errors can be corrected if $3t\leq n-l$. Also, one can use 
the Berlekamp-Welch algorithm \cite{../welch1986error} to correct the errors.\par

But Shamir secret sharing scheme is designed particularly to defend against passive adversaries and not 
against malicious adversaries. A class of threshold secret sharing schemes which are designed to defend 
against malicious adversaries is Verifiable Secret Sharing (VSS). There are many VSS schemes in the literature, 
and as of writing this report the efficient VSS schemes based on Shamir secret sharing are $\Pi_F$, 
$\Pi_P$ and $\Pi_{LA}$ \cite{../cryptoeprint:2023/1669} which are alternatives to the original VSS schemes 
from Feldman \cite{DBLP:conf/focs/Feldman87}, Pedersen \cite{../crypto-1991-1671} and the more recent 
ABCP \cite{../cryptoeprint:2023/992}. VSS schemes based on Shamir secret sharing allow shareholders to 
verify the correctness of the shares obtained during both the sharing and reconstruction phases. This enables 
these VSS schemes to defend against malicious adversaries who can actively corrupt $t$ parties as long as 
$t\leq\frac{n-1}{2}$. Publicly Verifiable Secret Sharing (PVSS) is an extension of VSS where anyone can 
verify the validity of the secret shares during the sharing phase. The main tools used in VSS and PVSS 
schemes are the \textbf{Sigma Protocols} which we overview in the next section \ref{sec:sigma-protocols}.

\section{Sigma Protocols}
\label{sec:sigma-protocols}
The agenda of this subsection is to give a brief formal background about some important primitives 
used in the PVSS ,$\Pi_S$ \cite{../cryptoeprint:2023/1669}, and the PPVSS ,$\Lambda_{RO}$ \cite{../cryptoeprint:2025/576}, schemes.
Let $X$ and $W$ be two sets with $R$ being a relation on $X\times W$, and $L=\{x\in X :\exists w\in W, xRw\}$
be the language defined by $R$ where $xRw$ says that $w$ is a witness for a given $x\in L$. 
Also, let $\mathcal{R}$ be a PPT algorithm such that $\mathcal{R}(1^\lambda)$ outputs pairs 
$(x,w)$ with $x\in L$ and $xRw$ where $\lambda$ is a security parameter.\par

Given a relation $R$ and its corresponding language $L$, a \textbf{Sigma ($\sum$) Protocol} 
is a $3$-round \textit{interactive} protocol between two Probabilistic Polynomial Time (PPT) algorithms, 
a prover $P$ 
and a verifier $V$. For some $x\in L$ with $xRw$, in the first round $P$ sends a 
commitment $a$ to $V$. To which $V$ sends a challenge $d$ to $P$ in the second round 
and finally $P$ responds back with the response $z$ to $V$ in the third round. 
$V$ outputs \textbf{true} or \textbf{false} upon the proof verification on transcript
$trans := (a, d, z)$. 
Informally, with a $\sum-$protocol a prover $P$ tries to convince
a verifier $V$ that they know a witness $w$ for a given statement $x\in L$ without 
revealing any information about $w$. To state it formally, a $\sum-$protocol is 
supposed to satisfy \textit{completeness}, \textit{Honest Verifier Zero Knowledge} (HVZK)
and \textit{Special Soundness} which are defined as follows.

\begin{definition}[Completeness]
  A $\sum-$protocol is said to be \textbf{complete} for $\mathcal{R}$ if
  the verifier $V$ always accepts the honest prover $P$ for any $x\in L$.
\end{definition}

\begin{definition}[HVZK]
  A $\sum-$protocol is said to be \textbf{HVZK} for $\mathcal{R}$ if there exist a PPT algorithm $S$ 
  that simulates $trans$ of the scheme corresponding to a given $x\in L$ with any witness $w$ of $x$. 
  That is, given $x\in L$,
  \begin{align*}
    trans(P(x,w)\leftrightarrow V(x)) &\approx trans(S(x) \leftrightarrow V(x))&& \text{, for any witness $w$ of $x$.}
  \end{align*}
  Where $trans(P(\cdot)\leftrightarrow V(\cdot))$ is the transcript of the $\sum-$protocol amongst 
  $P$ and $V$ and $\approx$ denotes the indistinguishability of the two transcripts.
\end{definition}

\begin{definition}[Special Soundness]
  A $\sum-$protocol is said to satisfy \textbf{Special Soundness} for $\mathcal{R}$, 
  if there exists a PPT extractor $\mathcal{E}$ for any two valid transcripts, $(a,d,z)$ and 
  $(a,d',z')$, corresponding to a given $x\in L$ with only a unique witness $w$ and $d\neq d'$ such that $\mathcal{E}(a,d,z,d',z')$ outputs the 
  witness $w$. 
\end{definition}

It is shown that a public-coin, complete, HVZK, special soundness $\sum-$protocol can be made into a
Non Interactive Zero Knowledge (NIZK) Proof of Knowledge (PoK) or Argument of Knowledge (AoK) in the 
Random Oracle ($RO$) model using Fiat-Shamir transform \cite{../10.1007/3-540-47721-7_12}. 
In the following subsections, we recall two important NIZK PoK schemes which are used in $\Pi_S$ and 
$\Lambda_{RO}$ schemes.

\subsection{Chaum-Pedersen Protocol for DL Equality}
\label{subsec:chaum-pedersen}
Recall $\mathbb{G}$ being the cyclic group of prime order $q$ with hard Discrete Logarithm (DL). 
For some $g,h\in \mathbb{G}$ consider the following relation:
\begin{align*}
  R_{DLEQ} &= \{(g,h,a,b),x : a=g^x, b=h^x\}.
\end{align*}
In \cite{../10.1007/3-540-48071-4_7}, Chaum and Pedersen proposed a NIZK PoK scheme for the DL Equality 
relation, $R_{DLEQ}$. Informally, a prover $P$ can convince a verifier $V$ that they know $x$ such that
it can be used with both $g$ and $h$ to obtain $a$ and $b$ respectively. This protocol is widely used in
many cryptographic applications like threshold decryption, e-voting and Randomness Beacons. 
We summarize the protocol in Figure \ref{../fig:chaum-pedersen}.
\input{../figures/chaum-pedersen.tex}

\subsection{NIZK PoK for Polynomial DL}
\label{subsec:polynomial-dl}
Recall $\mathbb{G}$ being the cyclic group of prime order $q$ with hard Discrete Logarithm (DL) and $g$ 
being its generator. Consider the following relation for some polynomial $f\in\mathbb{Z}_q[X]_t$ with
degree $t<n$:
\begin{align*}
  R_{PDL} &= \{(g,x_1,\dots,x_n,F(x_1),\dots,F(x_n)),f(X) : F(x_i)=g^{f(x_i)}, 1\leq i\leq n\}.
\end{align*}
In \cite{../cryptoeprint:2023/1669}, Baghery formally introduced a NIZK PoK scheme for the Polynomial DL 
relation, $R_{PDL}$, which is a generalization of Schnorr's ID protocol \cite{../crypto-1989-1727}. Informally, 
a prover $P$ can convince a verifier $V$ that they know a $t$ degree polynomial $f$ such that 
it can be used with $g$ to obtain $F(x_i)$ for $1\leq i\leq n$. This protocol is used to construct the PPVSS 
$\Lambda_{RO}$ \cite{../cryptoeprint:2025/576}, which was essential in building an efficient e-voting protocol. 
We summarize the protocol in Figure \ref{../fig:polynomial-dl}.
\input{../figures/polynomial-dl.tex}

In the next section we will give a brief overview of the Publicly Verifiable Secret Sharing (PVSS) and its 
security guarantees.



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End: 
