\documentclass[master=arc,british,oneside]{kulemt}
\ExpandArgs{NNo}\newcommand*\classversion{\fileversion}
\newcommand*\manualdate{2025-02-22}
\setup{title={Writing a Master's Thesis in LaTeX},
  subtitle={The `kulemt' v\classversion\ manual (\manualdate)},
  author={Luc Van Eycken},
  promotor={Prof.\,dr.\,ir. M.~Schevenels},
  assessor={Werkgroep masterproef},
  assistant={P. Wilson \and D. Knuth}}

%% Fonts 
%  - Select the main text and math fonts
%    Remember their names, so we can use them in the text
\usepackage{libertinus}
\newcommand*\rmfontname{Libertinus Serif}
\newcommand*\sffontname{Libertinus Sans}
\IfPackageLoadedTF{fontspec}%
  {%
    \usepackage{unicode-math}%
    \setmathfont{Libertinus Math}%
    \setmonofont{Latin Modern Mono}%
    \newcommand*\ttfontname{Latin Modern Mono}%
  }%
  {%
    \usepackage{libertinust1math}%
    \renewcommand{\ttdefault}{lmtt}%
    \newcommand*\ttfontname{Latin Modern Typewriter}%
    \DeclareUnicodeCharacter{1EBF}{\'{ê}}% For "Hàn Thế Thành"
  }
%  - Use microtype to enhance the typography
\usepackage{microtype}
%  - Generate an error for missing glyphs
\tracinglostchars=3

%% Biblatex for citations and annotated bibliography
\usepackage[style=numeric,abbreviate=false]{biblatex}
\addbibresource{refs.bib}
\DeclareFieldFormat{url}{\newline\nobreak\mkbibacro{URL}\addcolon\space\url{#1}}
\renewbibmacro*{urldate}{} % Do not print urldate
\DeclareFieldFormat{texdoc}{%
  Local documentation: \textcolor{teal}{\ttfamily texdoc #1}}
\DeclareFieldFormat{annotation}{#1}
\renewbibmacro{finentry}{\setunit{\finentrypunct}%
  \setunit{\par\nobreak}%
  \printfield{texdoc}%
  \setunit{\par\nobreak}%
  \printfield{annotation}%
  \finentry}
\DeclareSortingTemplate{nty}{%
  \sort{\field{presort}}%
  \sort[final]{\field{sortkey}}%
  \sort{% Entries with a missing name come first
    \field{sortname}%
    \field{author}%
    \field{editor}%
    \field{translator}%
    \literal{0}}%
  \sort{%
    \field{sorttitle}%
    \field{title}}%
  \sort{%
    \field{sortyear}%
    \field{year}}%
  \sort{%
    \field{volume}%
    \literal{0}}}
\newcommand*\citewithtitle[2][]{\citetitle{#2}~\cite[#1]{#2}}
\usepackage{metalogox}  % Better formatting of TeX, ... in bibliography

%% Additional formatting settings
%  - Use the chapter and headings styles as well as the ToC formatting
%    and the KU Leuven conventions as defined in the kulemtx document style.
%    Additionally it defines some extra user commands.
\usepackage[manual]{kulemtx}
%  - Lists are tighter than default
\firmlists
%  - Footnotes: set the marker flushleft and the text as a block paragraph
\setlength\footmarkwidth{1.5ex}
\setlength\footmarksep{0pt}
\footmarkstyle{\textsuperscript{#1}\hfill}
%  - URLs: Using \textlangle instead of \langle because \langle gives problems
%    under luatex with certain fonts (e.g. Latin Modern Mono).
\usepackage{url}
\ExplSyntaxOn
\cs_set_nopar:Npn \UrlLeft #1 \UrlRight{
  \tl_set:Nn \l_tmpa_tl {#1}
  \regex_replace_once:nnN { \A https?:// } {} \l_tmpa_tl
  \regex_replace_once:nnN { / \Z } {} \l_tmpa_tl
  \hbox:n { \rmfamily \small \textlangle }
  \l_tmpa_tl
  \hbox:n { \rmfamily \small \textrangle }
}
\ExplSyntaxOff

%% Additional packages
%  - subfigures
\newsubfloat{figure}
%  - tikz/pgf
%    Note: also loads xcolor
\usepackage{tikz}
\usetikzlibrary{arrows,calc}
%  - csquotes (needed by biblatex) !!! TODO: use it
\usepackage{csquotes}

%% Finally hyperref is loaded for proper PDF links
%  Colors: external links in blue, internal ones in dark blue
\usepackage[pdfusetitle,bookmarksnumbered]{hyperref}
\hypersetup{colorlinks,%
  filecolor={[rgb]{0,0,1}},urlcolor={[rgb]{0,0,1}},%
  citecolor={[rgb]{0,0,.75}},linkcolor={[rgb]{0,0,.75}}}
\pdfstringdefDisableCommands{\let\cs\textbackslash}

%% Define some typesetting commands
%  NOTE: Please don't use logos (\LaTeX ...) in the text, but simply LaTeX ...
\newcommand*\acro[1]{{%
    \ifdim\csname f@size\endcsname pt<10pt\else \expandafter\small\fi #1}\@}
\newcommand*\cls[1]{\textsf{#1}}
\newcommand*\pkg[1]{\textsf{#1}}
\newcommand*\env[1]{\cmdprint{#1}}
\newcommand*\opt[1]{\texttt{#1}}
\newcommand*\file[1]{\texttt{#1}}
\newcommand*\prog[1]{\texttt{#1}}
\newcommand*\PDF{\acro{PDF}}
\newcommand\Dutch[1]{`\foreignlanguage{dutch}{#1}'}
\newcommand\English[1]{`\foreignlanguage{english}{#1}'}
\newcommand*\NewInVersion[1]{%
  \sidepar{\small\textcolor{gray}{New in v#1}}\ignorespaces}

\begin{document}

\begin{preface}
  I would like to thank everybody who has kept me busy with writing, debugging,
  and documenting this LaTeX document class. My thanks goes especially to my
  supervisor and my assistant-supervisors. I also thank my assessors, at least
  those who read this text.

  Finally I would like to thank all the people who provided feedback,
  either with bug reports or by suggesting improvements.
\end{preface}

\tableofcontents

\begin{abstract}
  This document describes the use of the LaTeX document class \cls{kulemt},
  which implements the KU~Leuven Faculty of Engineering Science guidelines for
  writing a master's thesis. Since there are slight differences between the
  actual guidelines of the different engineering master's programmes, this
  class implements not only the common part, but it also provides the necessary
  options to adapt it to the specific requirements. So please check the
  guidelines of your master's programme before using or tweaking typesetting
  options.

  To illustrate the difference between the main text language and the master's
  programme language, this document is written in English (as the main text
  language) for a Dutch master's programme.

  This manual (dated \manualdate) describes the \cls{kulemt} class
  version~\classversion.
\end{abstract}

\begin{abstract*}
  Dit document beschrijft de LaTeX-documentklas \cls{kulemt}, die de
  richtlijnen van de Faculteit Ingenieurswetenschappen van de KU~Leuven
  voor het schrijven van een masterproeftekst implementeert. Maar vermits
  de richtlijnen van de verschillende ingenieursopleidingen licht
  verschillen, voorziet de documentklas de nodige opties om het resultaat
  aan te passen. Hou dus bij het aanmaken van de tekst niet zozeer rekening
  met wat de documentklas toelaat, maar wel met wat jouw master als
  specifieke richtlijnen opgeeft.

  Voor studenten van een Nederlandstalige master die hun masterproef in het
  Engels schrijven (bv.\ Erasmus-studenten) is een Nederlandse samenvatting
  verplicht. Als jouw master een uitgebreide samenvatting verlangt met
  figuren en tabellen kun je die best voorzien als een bijlage. Anders
  volstaat deze samenvatting van 1~bladzijde.

  Om het effect van twee talen te illustreren is dit document geschreven
  als een Engelse tekst (verder \English{text language} genoemd) voor een
  Nederlandstalige master (verder \English{master's programme language}
  genoemd).

  Deze handleiding van \manualdate\ beschrijft de LaTeX-documentklas
  \cls{kulemt} versie~\classversion.
\end{abstract*}

\listoffiguresandtables

\mainmatter

\include{inlatex}
\include{class}

\appendix
\appendixpage*

\include{masters}
\include{template}

\backmatter
\include{terminology}

\defbibnote{intro}{%
  Local documentation can be accessed from the command line using the
  \prog{texdoc} programme (\prog{mthelp} on a MikTeX installation). That
  local documentation corresponds to the packages installed on your system. The
  most recent documentation can be found online using the \acro{URL}.
  \bigskip
}
\printbibliography[heading=bibnumbered,prenote=intro]

\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-PDF-mode: t
%%% TeX-master: t
%%% ispell-local-dictionary: "british"
%%% End: 
